INLA replication

### 2022-09-15 src/example_inla-replication/inla-replication.Rmd
Remove some broke tex

<!-- Taking negative logs (to incorporate $f$) gives -->
<!-- \begin{equation*} -->
<!-- - \log p(\btheta \, | \, \y) \sim f(x, \btheta) + \log p(x \, | \, \btheta, \y) -->
<!-- \end{equation*} -->

@@

<!-- *Note: Does `TMB` keep the $-\frac{n}{2} \log(2\pi)$ constant here $-\log L^\star_f(\btheta) = -\frac{n}{2} \log(2\pi) + \frac{1}{2} \log \det (Q^\star(\btheta)) + f(\bm{\mu}^\star(\btheta), \btheta)$?* -->

@@

Probably going to need $Q^\star(\btheta)$ ($n \times n$ precision matrix) and $\bm{\mu}^\star(\btheta)$ ($n \times 1$ mean vector).
For example, the most basic version of the full conditional would be the Gaussian approximation
\begin{equation}
\tilde p(x_i \, | \, \btheta, \y) = \mathcal{N}(x_i \, | \, \mu^\star_i(\btheta), 1 / q^\star_i(\btheta)).
\end{equation}

Precision matrix $Q^\star(\btheta)$ is the Hessian of the negative logarithm of the posterior evaluated at $\bm{\mu}^\star(\btheta)$, having $(i, j)$th entry
\begin{equation}
Q^\star(\btheta)_{i, j} = - \frac{\partial^{2} \log p(x \, | \, \btheta, \y)}{\partial x_{i} \partial x_{j}} \Big\rvert_{x = \bm{\mu}^\star(\btheta)}
\end{equation}

>>>>

<!-- Taking negative logs (to incorporate $f$) gives -->
<!-- \begin{equation*} -->
<!-- - \log p(\theta \, | \, y) \sim f(x, \theta) + \log p(x \, | \, \theta, y) -->
<!-- \end{equation*} -->

@@

<!-- *Note: Does `TMB` keep the $-\frac{n}{2} \log(2\pi)$ constant here $-\log L^\star_f(\theta) = -\frac{n}{2} \log(2\pi) + \frac{1}{2} \log \det (Q^\star(\theta)) + f(\mu^\star(\theta), \theta)$?* -->

@@

Probably going to need $Q^\star(\theta)$ ($n \times n$ precision matrix) and $\mu^\star(\theta)$ ($n \times 1$ mean vector).
For example, the most basic version of the full conditional would be the Gaussian approximation
\begin{equation}
\tilde p(x_i \, | \, \theta, y) = \mathcal{N}(x_i \, | \, \mu^\star_i(\theta), 1 / q^\star_i(\theta)).
\end{equation}

Precision matrix $Q^\star(\theta)$ is the Hessian of the negative logarithm of the posterior evaluated at $\mu^\star(\theta)$, having $(i, j)$th entry
\begin{equation}
Q^\star(\theta)_{i, j} = - \frac{\partial^{2} \log p(x \, | \, \theta, y)}{\partial x_{i} \partial x_{j}} \Big\rvert_{x = \mu^\star(\theta)}
\end{equation}
